### 2015-07-08 thesis/thesis/chap1/chap1.tex
changes

In order to address the centralized decision making process limitations and adopt a distributed decision making approach, we introduce DDM, a Distributed Decision Making model for community formation. DDM regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining. Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities. The advantage of this approach is that the tree, which is initially created from the past data, reflects a comprehensive vision about agents' attitudes in terms of their action selection based on their past experiences. Moreover, the tree is getting continuously updated based on both new received feedback and the outcome of chosen actions. This continuous update makes the approach adapted to any change in the environment.
%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems.
The decision model provides web services with enough information which helps those services efficiently decide and predict the outcome of their different possible collaborations. This model works in a distributed manner in which services are self-sufficient in their decision making and do not rely on a centralized decision making process. Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join. The proposed model can be seen as a recommneder system that suggests beneficial actions for both communities and single services. Communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact both their short-term and long-term goals; therefore, opting for the best decision available.

>>>>

In order to address the centralized decision making process limitations and adopt a distributed decision making approach, we introduce DDM, a Distributed Decision Making model for community formation. DDM regulates web service agents' decision making process in terms of cooperating and deciding which group to join and which service to invite for joining. Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities. The advantage of this approach is that the tree, which is initially created from the past data, reflects a comprehensive vision about agents' attitudes in terms of their action selection based on their past experiences. Moreover, the tree is getting continuously updated based on both new received feedback and the outcome of chosen actions. This continuous update makes the approach adapted to any change in the environment.
%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems.
The decision model provides web services with enough information which helps those services efficiently decide and predict the outcome of their different possible collaborations. This model works in a distributed manner in which services are self-sufficient in their decision making and do not rely on a centralized decision making process. Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join. The proposed model can be seen as a recommneder system that suggests beneficial actions for both communities and single services. Communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact both their short-term and long-term goals; therefore, opting for the best decision available.

### 2015-07-08 thesis/thesis/chap2/chap2.tex
changes

        In this research work, we will use game theory to
        propose a cooperative game model for the aggregation of web
        services within communities. The solution concepts of our
        cooperative game seeks to find efficient ways of forming
        coalitions (teams) of web services so that they can maximize their
        gain and payoff, and distribute the gain in a fair way among all
        the web services. Achieving Fairness when the gain is distributed
        among the community members is the main factor to keep the
        coalition stable as no web service will expect to gain better by
        deviating from the community. In other words, the coalition is made
        efficient if all the members are satisfied. We first propose a
        representation function for communities of web services based on
        their QoS attributes. By using this function, we can evaluate the
        $worth$ of each community of web services. When facing new
        membership requests, a typical community master checks whether the
        new coalition having the old and new set of web services will keep
        the community stable or not. The community master will reject the
        membership requests if it finds out that the new coalition would
        be unstable, preventing $any$ subset of web services from gaining
        significantly more by deviating from the community and joining
        other communities or forming new ones. The computation of
        solutions for cooperative game theory problems is combinatorial in
        nature and proven to be NP-complete \cite{Algorithmic}, making
        this computation impractical in real world applications. However,
        using the concepts of coalition stability, we propose
        approximation algorithms running in polynomial time providing web
        services and community masters with applicable and near-optimal
        decision making mechanisms.

>>>>

In this research work, as the first contribution we will tackle with the issue of community formation in an efficient way for all the web service and communities involved. We will use game theory to propose a cooperative game model for the aggregation of web services within communities. The solution concepts of our cooperative game seeks to find efficient ways of forming coalitions (teams) of web services so that they can maximize their gain and payoff, and distribute the gain in a fair way among all the web services. Achieving Fairness when the gain is distributed among the community members is the main factor to keep the coalition stable as no web service will expect to gain better by deviating from the community. In other words, the coalition is made efficient if all the members are satisfied. We first propose a representation function for communities of web services based on their QoS attributes. By using this function, we can evaluate the $worth$ of each community of web services. When facing new membership requests, a typical community master checks whether the new coalition having the old and new set of web services will keep the community stable or not. The community master will reject the membership requests if it finds out that the new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more by deviating from the community and joining other communities or forming new ones. The computation of solutions for cooperative game theory problems is combinatorial in nature and proven to be NP-complete \cite{Algorithmic}, making this computation impractical in real world applications. However, using the concepts of coalition stability, we propose approximation algorithms running in polynomial time providing web services and community masters with applicable and near-optimal decision making mechanisms.

Next we will tackle the issue of distributed model of web services and propose a decision model for scenarios where information is incomplete. We proposed a training model for the problem of membership management of communities of web services. Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves. This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available. The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms. The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.

In our last contribution, the focus is on internal community management. We proposed a game-theoretic based model to analyze the best efficiency characteristics for the active services in open networks. The proposed framework considers the chances of web services in joining a community in different cases with truthful and lying information service agents. The proposed game analyzes the existing Nash equilibrium and situations where the maximum payoff is obtained.

### 2015-07-08 thesis/thesis/chap3/chap3.tex
changes

In this chapter,

>>>>

In this section, we proposed a cooperative game theory-based model for the aggregation of web services within communities. The goal of our services is to maximize efficiency by collaborating and forming stable coalitions. Our method considers stability and fairness for all web services within a community and offers an applicable mechanism for membership requests and selection of web services. The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more
tasks with high quality. Simulation results show that our, polynomial in complexity, approximation algorithms provide web services and community owners with applicable and near-optimal
decision making mechanisms.

As future work in this area, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications. From web service perspective, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperating game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.

In this chapter, we assumed our web services and communities have compelte knowledge of all the other web services and their parameters. In next section we propose distributed decision making model which can perform in scenarios where information is incomplete.

### 2015-07-08 thesis/thesis/chap5/chap5.tex
changes

In this chapter,

>>>>

In this chapter, we proposed a game-theoretic based model to analyze the best efficiency characteristics for the active services in open networks. The proposed framework considers the chances of web services in joining a community in different cases with truthful and lying information service agents. The proposed game analyzes the existing Nash equilibrium and situations where the maximum payoff is obtained.

Our model has the advantage of being simple and taking into account three important factors: (1) rational services seek better status in the environment by joining the community; (2) rational information service agents obtain higher payoff by truth telling; and (3) the community is obtaining more effective web services while the information service agents challenge for providing truthful information. As future work, we plan to consider the user role in the game to obtain more accurate results when users act rationally. Moreover, we would like to achieve a collusion resistant efficiency mechanism, which is still an open problem in open environments.

### 2015-07-08 thesis/thesis/chap6/chap6.tex
changes

\item F. Al-Saqqar, J. Bentahar, K. Sultan, W. Wan, E. Khosrowshahi Asl:, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.

@@

\item H. O. Marey, J. Bentahar, E. Khosrowshahi Asl, M. Mbarki, R. Dssouli, "Agents' Uncertainty in Argumentation-based Negotiation: Classification and Implementation", ANT/SEIT, Hasselt, Belgium, 2014.

\item H. Fallatah, J. Bentahar, E. Khosrowshahi Asl, "Social Network-Based Framework for Web Services Discovery", IEEE  FiCloud, Barcelona, Spain, 2014.

>>>>

%\item F. Al-Saqqar, J. Bentahar, K. Sultan, W. Wan, E. Khosrowshahi Asl:, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.

@@

%\item H. O. Marey, J. Bentahar, E. Khosrowshahi Asl, M. Mbarki, R. Dssouli, "Agents' Uncertainty in Argumentation-based Negotiation: Classification and Implementation", ANT/SEIT, Hasselt, Belgium, 2014.

%\item H. Fallatah, J. Bentahar, E. Khosrowshahi Asl, "Social Network-Based Framework for Web Services Discovery", IEEE  FiCloud, Barcelona, Spain, 2014.
